Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Updates from Overleaf
Partially reapply lost commit 1ea831260218d31bd46713eeba862c80782e024a

The directories to be processed are stored in different libraries in Paris\footnote{\textcolor{green}{Citer les bibliothèques sources?} \joseph{est-ce nécessaire ici ? Est-ce que ça peut être dans une annexe ?}}. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).

@@

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V. Rice's
thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip} and the Character Error Rates (CER) are computed at the entry level
and at the global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

>>>>

The directories to be processed are stored in different libraries in Paris\footnote{\textcolor{green}{Citer les bibliothèques sources?} \joseph{est-ce nécessaire ici ? Est-ce que ça peut être dans une annexe ?}\nathalie{Oui totalement...}}. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).

@@

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols
(hands, crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V.
Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at the entry
level and at the global level defined as the ratio between the number of errors (insertions/deletions/substitutions)
over the reference text length.
